Differential expression analysis: A pipeline to analyse time-course gene expression data

### 2019-05-02 scripts/02_differential_expression_analysis.Rmd
Implementing consensus strategy

```{r, echo=FALSE, results="hide"}
# XXX FIXME
data = read.table(".results/quantile_normalized.txt") 
source("utils.R")
```
```{r}
splines_model = moanin::create_splines_model(meta, degrees_of_freedom=6)
```

@@

The next step is typically to run a differential expression analysis.

>>>>

```{r, echo=FALSE, results="hide"}
# XXX FIXME
data = read.table(".results/quantile_normalized.txt") 
source("utils.R")
```

@@

The next step is typically to run a differential expression analysis. Most of
`moanin`'s function rely on an object containing a number of information such
as the metadata and the splines model used.

```{r}
splines_model = moanin::create_splines_model(meta, degrees_of_freedom=6)
```
